### 2019-04-10 paper/paper.tex
figure formatting

To better visualize the status of inter-package dependencies, we constructed
a directed dependency graph using dependants as out-degrees and
dependencies as in-degrees. Based on this dependency graph, Figure \ref{outDegree}
displays the percentage of packages with various amounts of dependencies. 
[MIGHT NEED TO CHANGE BASED ON DATA: While the average number of dependencies 
of packages continues to increase, the percentage of packages with zero 
to three dependencies has actually increased since the end of the original paper's
reporting period \cite{Wittern:2016}. This suggests some changes to developer 
behaviour, likely either as a deliberate effort by programmers seeking to avoid the perils of 
complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
ways in which JavaScript is used for project development. [ADD EXACT VALUES]

@@

@@

\begin{figure*}
  \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
  \caption{\code{npm} rank (based on PageRank) of five packages with the lowest geometric mean per year}
  \label{ranksByYear}
\end{figure*}

>>>>

To better visualize the status of inter-package dependencies, we constructed
a directed dependency graph using dependants as out-degrees and
dependencies as in-degrees. Based on this graph, Figure \ref{outDegree}
displays the percentage of packages with various amounts of dependencies. 
[MIGHT NEED TO CHANGE BASED ON DATA: While the average number of dependencies 
of packages continues to increase, the percentage of packages with zero 
to three dependencies has actually increased since the end of the original paper's
reporting period \cite{Wittern:2016}. This suggests some changes to developer 
behaviour, likely either as a deliberate effort by programmers seeking to avoid the perils of 
complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
ways in which JavaScript is used for project development. [ADD EXACT VALUES]

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
  \label{outDegree}
\end{figure}

@@

\begin{figure*}
  \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
  \caption{\code{npm} rank (PageRank) of the five packages each year with the lowest geometric}
  \label{ranksByYear}
\end{figure*}
